Opening up the court (surface) in tennis grand slams

### 2019-02-20 contest/surface-type/paper-tennis.Rmd
final final commit
made a new graph for paper

The rest of this paper is organized as follows. In Section 2 we describe the grand slam tennis data and examine it at a high level.  In Section 2.2 we examine the data at a high level and use clustering methods to determine how the courts differ from one another.  In Section 3 we describe our models with (1) complete data with few features and (2) partial data with more features along with the results.  Finally in Section 4, we summarize our results and discuss future work.

@@

@@

@@

@@

>>>>

The rest of this paper is organized as follows. In Section 2 we describe the grand slam tennis data and examine it at a high level.  In Section 3 we describe our models with (1) complete data with few features and (2) partial data with more features along with the results.  Finally in Section 4, we summarize our results and discuss future work.

@@

```{r nadal-graph}
 ## NADAL COEF SIZE

df_n <- data.frame(coeff = names(step_model_n$coeff), ave = step_model_n$coeff, sd = sqrt(diag(vcov(step_model_n))))
df_n$player <- "Nadal"
```

@@

```{r federer-graph}

 ## federer

df_f <- data.frame(coeff = names(step_model_f$coeff), ave = step_model_f$coeff, sd = sqrt(diag(vcov(step_model_f))))
df_f$player <- "Federer"
```

@@

```{r williams-graph}
 ## WilliamsCOEF SIZE

df_w <- data.frame(coeff = names(step_model_w$coeff), ave = step_model_w$coeff, sd = sqrt(diag(vcov(step_model_w))))
df_w$player <- "Williams"
```

@@

```{r plot-individual-effects}
df <- rbind(df_n, df_w, df_f)
keep_coefs <- which(df$coeff %in% c("(Intercept)", "opponent_rank",
                                    "pct_ace", "pct_bp", "pct_netpt",
                                    "ave_serve_speed", "wue_ratio"))
df <- df[keep_coefs,]
ggplot(df, aes(x = coeff, y = ave, col = player)) +
  geom_errorbar(aes(ymin = ave - 2 *sd, ymax = ave + 2 * sd), position = "dodge", width = .3) + 
   my_theme +
  # coord_flip() +
  theme(axis.text.x=element_text(angle = 30, hjust = 1)) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = .4) + 
  ggtitle("Effects on Reference Court") +
  scale_color_brewer("",palette = "Dark2") +
  theme(legend.position = "bottom", legend.text=element_text(size=8),
        # legend.margin=margin(0, 0, 0, 0),
        legend.margin=margin(t = 0, unit='cm'),
        legend.box.margin=margin(-10,-10,-10,-10)) + 
  xlab("") + coord_flip() + 
  ylab("Estimate") +
  scale_x_discrete(labels = c("Intercept", "Opp. Rank", "% Aces", "% Break Points Won", "% Net Points Won", "Ave. Serve Speed", "Winner:UE"))
  guides(col = guide_legend(nrow=2))
  #ggsave("~/Documents/ref-courts-eff.pdf", width = 8, height = 6)
```

```{r}
df <- rbind(df_n, df_w, df_f)
keep_coefs <- which(df$coeff %in% c("(Intercept)", "opponent_rank",
                                    "pct_ace", "pct_bp", "pct_netpt",
                                    "ave_serve_speed", "wue_ratio"))
  ## Interaction Effects
df2 <- df[-keep_coefs,]
ggplot(df2, aes(x = coeff, y = ave, col = player)) +
  geom_errorbar(aes(ymin = ave - 2 *sd, ymax = ave + 2 * sd), position = "dodge", width = .3) + 
   my_theme +
  # coord_flip() +
  theme(axis.text.x=element_text(angle = 30, hjust = 1)) +
  ggtitle("Interaction Effects") +
  scale_color_brewer("",palette = "Dark2") +
  theme(legend.position = "bottom", legend.text=element_text(size=8),
        # legend.margin=margin(0, 0, 0, 0),
        legend.margin=margin(t = 0, unit='cm'),
        legend.box.margin=margin(-10,-10,-10,-10)) + 
  xlab("") +
  ylab("Estimate") + facet_grid(~player) + coord_flip() + 
  #scale_x_discrete(labels = c("Intercept", "Opp. Rank", "% Aces", "% Break Points Won", "% Net Points Won", "Ave. Serve Speed", "Winner:UE"))
  guides(col = guide_legend(nrow=2))
```
